## References {.appendix}

::: {#refs}
:::

## Attachments {.appendix}

The following files are associated with this report. `renv.lock` files can be used to re-create the R environment using `renv`. `.conda` files can be provided to create a conda environment.

```{r appendix-attachments}
#| echo: false
#| results: asis

Sys.getenv(x='REPORT_PATH', unset='unset report_path') |> cat(sep='\n')

Sys.getenv(x='REPORT_PATH', unset=getwd()) |>
	file.path('files') |>
	list.files() -> files
print(files)
if(length(files) > 0) {
	files |> (\(x) sprintf(fmt="{{< fa paperclip >}} [%s](files/%s)", x, x))() |> cat(sep="</br>")
} else {
	cat('No attachments to list.')
}
```

## Package information {.appendix}

[`renv`](https://github.com/rstudio/renv) was used to manage package versions for this analysis. The <a href="files/renv.lock" target="_blank">`renv.lock`</a> file can be used to recreate the package environment.

```{r appendix-session-info}
#| code-summary: Package versions that created this report
#| echo: false
sessioninfo::session_info()
```
